---
output:: rmarkdown::github_document
title:: "`tvthemes` : Themes and Color Palettes based on American TV Shows for `ggplot2` visualizations"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

What kick-started this whole package was my [blogpost]() looking at simple TV stats on my current favorite TV show, Brooklyn Nine-Nine. I got a lot of good feedback on the colors I used for the custom theme so I decided to expand it to other shows!

## Installation

```{r, eval=FALSE}
# install.packages(devtools)
devtools::install_github("Ryo-N7/tvthemes")
```


```{r, message=FALSE, warning=FALSE}
# devtools::install_github("Ryo-N7/tvthemes")
library(tidyverse)
library(tvthemes)
library(glue)
library(extrafont)
loadfonts()   # load fonts on your computer
```

## Fonts

```{r, eval=FALSE}
import_champion_htf_heavyweight()
import_simpsons()
import_theLastAirbender()
```


```{r}
import_champion_htf_heavyweight()
import_simpsons()
import_theLastAirbender()
```

## Brooklyn Nine-Nine

Bright colors for best contrast.

```{r}
options(scipen=999)  # turn-off scientific notation like 1e+48
data("midwest", package = "ggplot2")
ggplot(midwest, aes(x = area, y = poptotal)) + 
  geom_point(aes(col = state, size = popdensity)) + 
  geom_smooth(method = "loess", se = F, color = "black") + 
  xlim(c(0, 0.1)) + 
  ylim(c(0, 500000)) + 
  labs(subtitle = "Area Vs Population", 
       y = "Population", 
       x = "Area", 
       title = "New Retro Theme", 
       caption = "Source: midwest") + 
  theme_brooklyn99(title.size = 20) +
  scale_color_brooklyn99()
```

## b99 dark

Slightly more subdued colors.

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), 
                 col = "black", size = 0.1,
                 binwidth = 0.1) +
  scale_fill_brooklyn99_dark() +
  labs(title = "Brooklyn Nine-Nine! nikolaj, do you know what a clap back is ",
       subtitle = "because i do") +
  theme_brooklyn99(font.title = "Titillium Web Black",
                   font.text = "Roboto Slab") #+
  #theme(text = element_text(face = "bold"))
```


## p&r normal

```{r}
# mtcars %>% 
#   mutate(cyl = as_factor(cyl),
#          carb = as_factor(carb)) %>% 
  # ggplot(aes(mpg, hp)) +
  # #geom_point(aes(color = carb), size = 2) +
  # geom_col(fill = "#4C3114") + # "#549E39" lightgreen
  # geom_point(size = 2, color = "#7A491E") +   #  #4C3114 darker brown
  # geom_point(color = "yellow") +
  # geom_point(color = "#fee0d2") +
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  labs(title = "Parks and Recreation",
       subtitle = "blahblah Leslie Knope") +
  theme(text = element_text(family = "Champion HTF-Heavyweight"),
        plot.subtitle = element_text(color = "grey20"),
        axis.text = element_text(size = 8, color = "grey20"),
        axis.title = element_text(color = "grey20"),
        plot.background = element_rect(color = NA, fill = "#CCFFBB"),#238443   #CCFFBB
        panel.background = element_rect(color = NA, fill = "#238443"), # #1A5E1FFF darkgreen  #238443
        panel.grid.major = element_line(color = "#fee0d2"),
        panel.grid.minor = element_line(color = "#fee0d2")) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_fill_parksAndRec()
```

## p&r light

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  labs(title = "Parks and Recreation",
       subtitle = "blahblah Leslie Knope") +
  theme(text = element_text(family = "Champion HTF-Heavyweight", color = "#fee8c8"),
        axis.text = element_text(size = 8, color = "#fee8c8"),
        axis.title = element_text(color = "#fee8c8"),
        plot.background = element_rect(color = NA, fill = "#41ab5d"),#238443   #CCFFBB
        panel.background = element_rect(color = NA, fill = "#CCFFBB"), # #1A5E1FFF darkgreen  #238443
        panel.grid.major = element_line(color = "grey20"),
        panel.grid.minor = element_line(color = "grey20"),
        legend.title = element_text(color = "grey20"),
        legend.text = element_text(color = "grey20", size = 9)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_fill_parksAndRec()
```


### P&R logo

```{r}
library(shadowtext)
library(glue)

header <- ggplot() +
  geom_shadowtext(aes(y = 3.15, x = 2,
           family = "Champion HTF-Heavyweight"), 
           color = "#fcf7e8", size = 50,
           label = glue("Parks & Recreation")) +
  # annotate(geom = "text", y = 3.15, x = 2, size = 50, 
  #          family = "Champion HTF-Heavyweight", color = "#fcf7e8",
  #          label = glue("Parks & Recreation")) +
  geom_shadowtext(aes(y = 3.15, x = 2,
           family = "Champion HTF-Heavyweight"), 
           color = "#fcf7e8", size = 25,
           label = glue("Parks & Recreation")) +
  # annotate(geom = "text", y = 2.5, x= 2, size = 25, 
  #          family = "Champion HTF-Heavyweight", color = "white",
  #          label= "Parks & Recreation") +
  ylim(0, 4) +
  theme_void() +
  theme(plot.background = element_rect(color = "#fcf7e8", 
                                       fill = "#005502", # "#1A5E1FFF" "#CCFFBB"
                                       size = 5))
header
```



## The Simpsons

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  labs(title = "The Simpsons",
       subtitle = "Theme inspired in part by @nathancunn's blog posts",
       caption = glue("
                      A 'Bake 'em Away, Toys!' Production
                      Location: Sector 7G")) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_fill_simpsons() +
  theme_simpsons(title.size = 18)
```




## The Good Place

- Pobody's Nerfect t-shirt color scheme (yellow/purple/brown/darknavy)





## Rick & Morty

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  #geom_bar(fill = "#FFD235") +
  labs(title = "Rick and Morty",
       subtitle = "blahblah Gazorpazorp Summer goddamit") +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_fill_rickAndMorty() + 
  theme_minimal() +
  theme(text = element_text(family = "Get Schwifty"),
        plot.background = element_rect(color = NA, fill = "#ece5d3"), 
        panel.background = element_rect(color = NA, fill = "#ece5d3")) -> randm

ggsave("randm.png")
```

## Avatar: The Last Airbender theme

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  ggpomological::scale_fill_pomological() +
  # ggpomological::theme_pomological()
  # scale_fill_parksAndRec() +
  labs(title = "Avatar: The Last Airbender",
       subtitle = "Avatar State, Yip Yip!") +
  theme_theLastAirbender() -> tlatheme

tlatheme

ggsave("tlatheme.png")
```

```{r}
basic_iris_plot <- ggplot(iris) +
  aes(x = Sepal.Length, y = Sepal.Width, color = Species) +
  geom_point(size = 2)

basic_iris_plot +
  ggpomological::scale_color_pomological() +
  ggpomological::theme_pomological() -> basicpom

ggpomological::paint_pomological(basicpom)

ggsave("basicpom.png")
```



```{r}
scales::show_col(dutchmasters::dutchmasters$view_of_Delft)
scales::show_col(dutchmasters::dutchmasters$milkmaid)
scales::show_col(dutchmasters::dutchmasters$little_street)
```


```{r}
ggplot(diamonds, aes(color, fill = clarity)) +
  geom_bar() +
  dutchmasters::scale_fill_dutchmasters(palette = "staalmeesters") -> dmasters

ggsave("dmasters.png")
```


### Avatar: Fire Nation

Flameo, Hotman!

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  scale_fill_fireNation() +
  labs(title = "Flameo, Hotman!",
       subtitle = "Fire. Wang Fire. This is my wife, Sapphire.") +
  theme_theLastAirbender() -> flameo

flameo

ggsave("flameo.png")
```


### Avatar: Air Nomads

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  scale_fill_airNomads() +
  labs(title = "Let's head to the Eastern Air Temple!",
       subtitle = "Appa, Yip Yip!") +
  theme_theLastAirbender()
```


### Avatar: Water Tribe

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  scale_fill_waterTribe() +
  labs(title = "I am thinking maybe we could... do an activity together?",
       subtitle = "... Do an activity? :)") +
  theme_theLastAirbender(title.size = 8)
```



### Avatar: Earth Kingdom

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  scale_fill_earthKingdom() +
  labs(title = "There is no war in Ba Sing Se",
       subtitle = "(Welcome to Lake Laogai)") +
  theme_theLastAirbender() -> earthkingdom

earthkingdom

ggsave("earthkingdom.png")
```



## South Park


```{r}

```


## Spongebob Squarepants

```{r}
mpg %>% 
  ggplot(aes(displ)) +
  geom_histogram(aes(fill = class), col = "black", size = 0.1) +
  scale_fill_spongeBob() +
  labs(title = "F is for Fire that burns down the whole town!",
       subtitle = "U is for Uranium... bombs! N is for No survivors when you're-") +
  theme_spongeBob()
```



## tvthemes hex sticker

Creating the hex sticker for this package was done with the `hexSticker` package by ____. The image I chose was from [here](https://www.irasutoya.com/2017/07/blog-post_930.html) of a boy sitting way too close while watching TV. I would have liked to use something from one of the actual TV shows that appear in this package but don't know if that would violate copyright or something so I went with the safe option of using a free "irasutoya" picture.

```{r eval=FALSE}
library(hexSticker)
download.file("https://3.bp.blogspot.com/-kHda-2huAF8/WUdZKshMQkI/AAAAAAABFDM/sXt-PT9dKtYp2Y0Y_OV64TJzs7PvOLZmgCLcBGAs/s800/tv_boy_chikaku.png",
              destfile = paste0(tempdir() , ".png"), mode="wb")

sticker(subplot = paste0(tempdir() , ".png"), package = "tvthemes",
        p_size = 20, p_x = 1, p_y = 1.65, 
        p_color = "#8B4411", p_family = "Roboto Condensed",
        s_x = 1.0, s_y = .95,
        s_width = 0.6, s_height = 0.6, 
        h_fill = "#f5f5dc", h_color = "black",
        filename = "tvthemes_hexsticker.png")
```


```{r}
library(hexSticker)
library(magick)
library(extrafont)
loadfonts()

download.file("https://3.bp.blogspot.com/-kHda-2huAF8/WUdZKshMQkI/AAAAAAABFDM/sXt-PT9dKtYp2Y0Y_OV64TJzs7PvOLZmgCLcBGAs/s800/tv_boy_chikaku.png",
              destfile = paste0(tempdir() , ".png"), mode="wb")

sticker(subplot = paste0(tempdir() , ".png"), package = "tvthemes",
        p_size = 22, p_x = 1, p_y = 1.5, 
        p_color = "#8B4411", p_family = "Roboto Condensed",
        s_x = 1.0, s_y = .85,
        s_width = 0.6, s_height = 0.6, 
        h_fill = "#f5f5dc", h_color = "black",
        filename = "tvthemes_hexsticker.png") 

stickeroo <- image_read("tvthemes_hexsticker.png")
stickeroo2 <- stickeroo %>% image_scale("121x140")
image_write(stickeroo2, "logo.png")
```


![]()
